---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# polygenicPTSD

The goal of polygenicPTSD is to make an easy-to-use package for multi-center sites in the PGC-PTSD Physical Health Workgroup to conduct analysis on the interaction between PTSD and BP Polygenic Risk Score (PRS) in predicting various BP outcomes. It includes functions to ensure data has appropriate variables required for analysis, creates new variables which categorizes continuous BP into categorical hypertension outcomes based on old and new AHA criteria, stratifies data by ancestry, runs linear regressions on continuous BP outcomes and generalized linear models on categorical hypertension outcomes, and more. 

## Installation

You can install polygenicPTSD from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("margarethannum/PolygenicPTSD")
```

## Example

This is a basic example which shows you how to run the analysis pipeline on simulated data:

```{r example, message = FALSE, eval=FALSE}
#Load package and the packages it depends on (dplyr and nnet)
#install.packages("nnet", "dplyr") #if you need to install
library(polygenicPTSD)
library(dplyr)
library(nnet)

## STEP 1a Load and merge
## Load and merge data (or see example simulated data included with our 
## package)

data("merged_example")

## Replace STUDYPI below with last name of Principle Investigator (For example "Sumner")
study <- "StudyPI"

## STEP 1b Categorization
## Create dataframe with 7 new categorical variables for hypertension 
## classification, continuous BP adjustment for antihypertension use, 
## and ancestry (necessary for analysis)

classed <- htn_outcome_classify(merged_example)

## Create ancestry stratification indices

index_eur = grepl(0, classed$ancestry)
index_afr = grepl(1, classed$ancestry)

## STEP 1C Testing
## Fisher's test on old vs new AHA guideline classifications 
## stratified by ancestry

## Below functions all save output in working directory.
## We recommend you create a folder "results" and change your working directory to that location.

setwd("~/results/")

#Then run functions

## STEP 2
## Linear regression analysis for continuous outcomes (SBP & DBP)
polygenicPTSD_contin(classed)

## Logistic regression analysis for binary hypertension outcomes 
## (non-hypertensive & hypertensive)

## STEP 3
## Multinomial and logistic regression for categorical HTN outcome
polygenicPTSD_logit(classed)

## Multinomial regression analysis for 3-level hypertension outcomes 
## (normotensive, pre-hypertensive & hypertensive)

polygenicPTSD_multinom(classed)

## For any questions on documentation refer to full pipeline document 
## and/or type: ?function to see help documentation

?merged_example
?polygenicPTSD_logit


```
